Paper 1: Triangulating trends in inequality around the world from secondary databases

### 2023-01-08 PhD_pages/data_appendices/1_B_within_country_trends.qmd
Shifting data prep for Paper 1 to appendix

---
title: Shinylive in Quarto example
format: html
filters:
  - shinylive
---

This is a Shinylive application embedded in a Quarto doc.

These are Shiny for Python applications which run completely in the browser, using Pyodide (Python compiled to WebAssembly).

See the [Shilylive quarto extension](https://github.com/quarto-ext/shinylive) for further documentation.

And the documentation on [Shiny for Python](https://shiny.rstudio.com/py/docs/putting-it-together.html).

```{shinylive-python}
#| standalone: true

from shiny import *

app_ui = ui.page_fluid(
    ui.input_slider("n", "N", 0, 100, 40),
    ui.output_text_verbatim("txt"),
)

def server(input, output, session):
    @output
    @render.text
    def txt():
        return f"The value of n*2 is {input.n() * 2}"

Here is a second app I am testing:

>>>>

---
title: "Appendix 1.B: Analysing global trends in within-country inequality"
format: html
warning: false
filters:
  - shinylive
---

A key difficulty of comparing trends is that the data is incomplete coverage. The paper uses two methods to calculate and compare aggregate within-country trends across incomplete data: using reference years and using year fixed effects in a regression.

## Method 1: Reference years

I need to allow for the income/consumption issue (currently the data includes both – i.e. multi observations per country year).

## Method 2: regression analysis

## Explore the date

I plan to build a Shiny app to help compare trends across datasets (using Shinylive – built on Shiny for Python - ).

Here is a test app just so I can test the wiring of how such an app works.

### 2023-01-08 PhD_pages/paper_pages/paper1.qmd
Shifting data prep for Paper 1 to appendix

---
title: "Paper 1: Triangulating trends in inequality around the world from secondary databases"
---

@@

::: {.callout-note collapse="true" appearance="minimal"}
### Load PIP data

```{r}
# df_pip<- read.csv("https://raw.githubusercontent.com/owid/poverty-data/main/datasets/pip_dataset.csv")

df_pip<- read.csv("PhD_pages/data/pip_dataset (2).csv")

df_pip<- df_pip %>%
  filter(ppp_version == 2017) %>%
  rename("Gini" = "gini",
         "Top_10_share" = "decile10_share",
         "Entity" = "country",
         "Year" = "year")

# drop subnational data where national data is available
df_pip<- df_pip %>%
  filter((!Entity %in% c("China", "India", "Indonesia")) | reporting_level == "national")

# drop income if both income and consumption are available
df_pip<- df_pip %>%
  group_by(Entity, reporting_level, Year) %>%
  mutate(n = n()) %>%
  filter(n<2 | welfare_type == "consumption") %>%
  ungroup()

 #drop regional aggregates
drop_aggs<- c(
  "East Asia and Pacific",
  "Europe and Central Asia",
  "High income countries",
  "Latin America and the Caribbean",
  "Middle East and North Africa",
  "Sub-Saharan Africa",
  "World"
)

df_pip<- df_pip %>%
  filter(!Entity %in% drop_aggs)

@@

::: {.callout-note collapse="true" appearance="minimal"}
### Load WID data

```{r}
# df_wid<- read.csv("https://raw.githubusercontent.com/owid/notebooks/main/BetterDataDocs/PabloArriagada/WID/data/final/wid_pretax.csv")

df_wid<- read.csv("PhD_pages/data/wid.csv")

df_wid<- df_wid %>%
  rename("Gini" = "Gini.coefficient",
         "Top_10_share" = "P90.P100...share.of.the.top.10.")

drop_entities<- c(
"China - rural",
"China - urban",
"East Germany",
"Other Russia and Central Asia",
"Other East Asia",
"Other Western Europe",
"Other Latin America",
"Other MENA",
"Other South & South-East Asia",
"Other Sub-Saharan Africa",
"Africa",
"Asia",
"Europe",
"Oceania",
"Central Asia",
"East Africa",
"East Asia",
"Eastern Europe",
"Middle Africa",
"North Africa",
"North America",
"South-East Asia",
"South Africa region",
"West Africa",
"West Asia",
"Western Europe",
"European Union",
"World",
"Asia (excluding Middle East)",
"North America and Oceania",
"Sub-Saharan Africa",
"Latin America",
"Middle East",
"MENA",
"Russia and Central Asia",
"South & South-East Asia"
)

df_wid<- df_wid %>%
  filter(!Entity %in% drop_entities)
```

@@

::: {.callout-note collapse="true" appearance="minimal"}
### Standardize coutry names across datasets
```{r}

pip_countries<- df_pip %>%
  select(Entity) %>%
  unique() %>%
  mutate(Entity_pip = Entity)

wid_countries<- df_wid %>%
  select(Entity) %>%
  unique() %>%
  mutate(Entity_wid = Entity)

countries<- full_join(pip_countries, wid_countries, keep = TRUE) %>%
  select(Entity_pip, Entity_wid)

Countries that are in the PIP data but not the WID data:
```{r}
kable(
  countries %>%
       filter(is.na(Entity_wid))
)
```
Countries that are in the WID data but not the PIP data:
(TO-DO: drop regions and sub-national data from the WID data at an eariler step.)
```{r}
kable(
  countries %>%
       filter(is.na(Entity_pip))
)
```
:::

>>>>

---
title: "Paper 1: Triangulating trends in inequality around the world from secondary databases"
format: html
---

@@

@@

@@
